Secondary analyses (appendices)

### 2025-08-05 _manuscript/analysis/secondary_analyses.qmd
commit quarto manuscript website for preprint version 2

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(statistic = case_match(statistic, "chisq.scaled" ~ "$\\chi^2$", "pvalue.scaled" ~ "$p$", "df.scaled" ~ "$df$", "cfi.scaled" ~ "CFI", "rmsea.scaled" ~ "RMSEA", "srmr" ~ "SRMR")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  mutate(est_print = if_else(statistic == "df", as.character(est), est_print)) |>
  mutate(est_print = if_else(statistic == "p", papaja::printp(as.numeric(est_print)), est_print)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)

>>>>

fit_df <- bind_rows(
  data.frame(as.list(fitMeasures(fit1A6))) |> mutate(measure = "age", categories = "6"),
  data.frame(as.list(fitMeasures(fit1A2))) |> mutate(measure = "age", categories = "2"),
  data.frame(as.list(fitMeasures(fit1G6))) |> mutate(measure = "height", categories = "6"),
  data.frame(as.list(fitMeasures(fit1G2))) |> mutate(measure = "height", categories = "2"),
  data.frame(as.list(fitMeasures(fit1Ge6))) |> mutate(measure = "weight", categories = "6"),
  data.frame(as.list(fitMeasures(fit1Ge2))) |> mutate(measure = "weight", categories = "2")
) |>
  pivot_longer(!c(measure, categories), names_to = "statistic", values_to = "est") |>
  filter(statistic %in% c("chisq.scaled", "pvalue.scaled", "df.scaled", "cfi.scaled", "rmsea.scaled", "srmr")) |>
  mutate(statistic = case_match(statistic, "chisq.scaled" ~ "$\\chi^2$", "pvalue.scaled" ~ "$p$", "df.scaled" ~ "$df$", "cfi.scaled" ~ "CFI", "rmsea.scaled" ~ "RMSEA", "srmr" ~ "SRMR")) |>
  mutate(est_print = papaja::printnum(est, gt1 = FALSE, digits = 3)) |>
  mutate(est_print = if_else(statistic == "$df$", as.character(est), est_print)) |>
  mutate(est_print = if_else(statistic == "$p$", papaja::printp(as.numeric(est_print)), est_print)) |>
  pivot_wider(id_cols = statistic, names_from = c(measure, categories), values_from = est_print)
